Model Adaptivity for Goal-Oriented Inference using Adjoints

### 2016-11-26 paper/numerical_experiments_v3_cmame.tex

\section{Numerical Experiments}\label{sec:numexp}
%
We now use \cref{alg:refSeries} to solve goal-oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \cref{sec:errLocal}. We first consider two-dimensional models in order to explore the behavior of the algorithm as well as the effect of varying the placement of observations and QoI regions. In \cref{sec:cdvcdr}, the high-fidelity model is a convection-diffusion-reaction nonlinear model, and the low-fidelity model is a linear convection-diffusion model. We apply \cref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region. In \cref{sec:constvfield}, both the high- and low-fidelity models are convection-diffusion-reaction nonlinear models, but they differ in how the parameter is represented. In \cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models, again targeting a convection-diffusion-reaction problem.

@@

%------------------------------------------------------------------------------------------------------------------------%
\subsection{Variable Physics: Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
%------------------------------------------------------------------------------------------------------------------------%
In this section, we consider a pair of models which differ in the physics included. In \cref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem. \Cref{sec:cdvcdrBaseRef} describes the results of applying \cref{alg:refSeries} to the baseline problem, and \cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
%
%------------------------------------------------------------%
\subsubsection{Problem Setup} \label{sec:cdvcdrSetup}
%------------------------------------------------------------%
%
We consider a rectangular domain $\Omega(x_1,x_2)=[0,5]\times[0,1]$, where $x_1$ and $x_2$ are the spatial coordinates. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by,
%
\begin{subequations}
\label{eq:cdvcdrHF}
\begin{align}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:cdvcdrHF_int} \\
u = 0 \quad &\text{on } \partial \Omega, \label{eq:cdvcdrHF_bdry}
\end{align}
\end{subequations}
%
where the state $u$ is the species concentration and $f(q)$ is a forcing field described by the parameters. We have a divergence-free parabolic-profile velocity field $\vec{V}(x_1,x_2) = (2x_2(1-x_2),0)$; the diffusion and reaction coefficients are $k_d = 0.1$ and $k_r = -42.0$, respectively. The low-fidelity model,
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u = f(q)
\end{equation}
%
differs only in the removal of the reaction term. To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively. The resulting mixed-fidelity models can be described by,
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k^{MF}_ru^2= f(q),
\end{equation}
%
where $k^{MF}_r$ is a piecewise-constant reaction coefficient,
%
\begin{equation}
k^{MF}_r=
\begin{cases}
k_r & \textrm{if }x\in\Omega_{HF} \\
0 & \textrm{if }x\in\Omega_{LF}.
\end{cases}
\end{equation}
%
Homogeneous Dirichlet boundary conditions are applied on the entire boundary of the domain. The QoI we wish to calculate is the integral of the state,
%
\begin{equation}
I(q,u)=\int_{(x_1,x_2)\in \Omega_I} u \:\textrm{d}A,
\end{equation}
%
over a region $\Omega_I=[0.625,0.875]\times[0.375,0.625]$.

The unknown parameters to be inferred correspond to the forcing field, so that in this case $f(q)=q$. The observations are sparse measurements of the state.
\cref{fig:baseSetup} shows the locations of the observations and the region $\Omega_I$ over which the QoI is calculated. For the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters). Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term in the objective function \cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
\caption{Locations of the observations and the QoI region.}
\label{fig:baseSetup}
\end{figure}
%

@@

We now present the results for solving the inference problem using \cref{alg:refSeries}. Once the QoI error estimate is calculated using \cref{eq:finErrExp}, the error estimate is then decomposed into local contributions. At each iteration, based on this decomposition, we choose the basis functions with the largest error contributions until an additional 5\% of the elements has been marked for refinement. This is repeated until the estimated absolute relative error in the QoI, calculated as $\epsilon_i/(\epsilon_i+I(q_{MF_i},u_{MF_i}))$, is less than $1\%$.

@@

We see that the largest local error contributions are concentrated in the QoI region and around the observation location closest to the QoI. In the first decomposition of the error (\cref{fig:baseRef0}), the region where the elemental error is greatest is around the leftmost observation location. Since the constraining model is an elliptic PDE, with weak convection, information flow is localized, and is weakly convected from left to right. Therefore, for the calculation of the QoI, it is most important to refine the region near the leftmost observation location, and then around the QoI region. After that, the error decomposition suggests refinement in regions upstream and around the middle observation location, and then the rightmost observation location.

\Cref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by \cref{alg:refSeries}; the true and estimated relative errors are calculated relative to the true and estimated high-fidelity QoI, respectively. In this case, we see that QoI error of $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain. We note that while here the error is seen to decrease with increasing refinement, in general there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
\label{fig:baseErr}
\end{figure}
%

@@

\cref{fig:qoiStudy} shows the domain for three cases considered, with the same set of observations but increasingly large, nested QoI regions $\Omega_I$.
The error decompositions for each case are also shown in \cref{fig:qoiStudy}. The bottom row gives the baseline case presented in \cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, rather than only enough basis functions to cover 5\% of the domain in their support, so the proportion of elements marked for refinement in each iteration will be slightly larger than in \cref{sec:cdvcdrBaseRef}.
% KW: I don't understand this last sentence. What's the difference with Section 4.1.2?
Although refinement is still most important around the observation location closest to $x_1=0$, as the QoI region expands the other two observation locations become more important in that the error decomposition suggests refinement around them earlier. As the QoI region expands, it is also more clearly noticeable that refinement is not equally important in all parts of the QoI region.

\begin{figure}[htbp]
\centering
\captionsetup{justification=centering}
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
  \includegraphics[width=0.21\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.png}
  \label{subfig:obsSetup}
}
\captionsetup{justification=centering}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err0_nobar.png}
  \label{subfig:obsLF}
}
\captionsetup{justification=centering}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.png}
}
\captionsetup{justification=centering}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2_barnorm.png}
  \label{subfig:obsMFlast}
}
  \caption{Effects of increasing the QoI region. Column \protect\subref{subfig:obsSetup2}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF2}--\protect\subref{subfig:obsMFlast2}): the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
  \label{fig:qoiStudy}
\end{figure}

\cref{fig:dataStudy} shows another set of cases considered, now with the same QoI region $\Omega_I$ but with increasing, nested sets of observations.
The error decomposition for the three cases is shown in \cref{fig:dataStudy}. The bottom row is the same as that in \cref{fig:qoiStudy}. Refinement appears to be consistently most important around the observation location closest to $x_1=0$ and the QoI region. However, as more observation locations are added, it becomes no longer necessarily true that refinement becomes less important around observation locations as their distance from the QoI region increases. In the second and third rows, one can see that after the areas around the QoI region and the two closest observation locations have been refined, the next area to be refined is not around the third closest observation location, but rather around one near the middle of the domain. This suggests that interactions between observation locations and the QoI may be non-intuitive, and in these cases a rigorous method for forming a mixed-fidelity model would be most helpful. % KW: I don't understand a lot of this discussion. You need to explain to me what you mean.

@@

We consider the same high-fidelity model as in \cref{sec:cdvcdr}:
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
\end{equation}
with the same diffusion coefficient $k_d = 0.1$  and reaction coefficient $k_r = -42$. The low-fidelity model
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
\end{equation}
differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field. The intermediate mixed-fidelity models thus have parameter fields that are constant over the subregions of the domain where the low-fidelity model is used. For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold. The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in \cref{sec:cdvcdr}. As the inverse problem is ill-posed, except when the low-fidelity model is used throughout the domain, regularization is used; the Tikhonov regularization term in \cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.

@@

As with the previous examples in \cref{sec:cdvcdr}, the decomposition of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model. The number of degrees of freedom in the inverse problem increases with the proportion of the domain in which the high-fidelity model is used. With each iteration, an additional $10\%$ of the elements are marked for refinement. This is repeated until the estimated absolute relative error in the QoI is less than $1\%$.

\Cref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated. 
%
\begin{figure}[htbp]
\centering
\subfloat[MF$_0$ ($0\%$ HF)]{
	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_LF_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_LF.png}
} \\
\subfloat[MF$_1$ ($10\%$ HF)]{
	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF01_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF01.png}
} \\
\subfloat[MF$_2$ ($20\%$ HF)]{
  \includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF02_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF02.png}
} \\
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF03.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_3$ ($30\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF04.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_4$ ($40\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF05.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_5$ ($50\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
\subfloat[MF$_6$ ($60\%$ HF)]{
	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF06_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF06.png}
}
\caption{Left: Multi-fidelity refinement over the domain (low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion). Right: local error contributions. The (weighted) residual, and thus the local error contribution, tends to spike sharply at the interface between the low- and high-fidelity regions; the color range is truncated to make the error distribution visible elsewhere in the domain.}
\label{fig:svfRef}
\end{figure}
%
Comparing to \cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest observation location; here, all three observation locations and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration. This reflects the global nature of the differences between the low- and high-fidelity models.

The corresponding true and estimated absolute errors in the QoI are shown in \cref{fig:svfErr}.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.}
\label{fig:svfErr}
\end{figure}
%
In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI. The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain. We also see that in this case, in contrast to the example in \cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.

@@

In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of \cref{alg:refSeries}, they are both simple enough and similar enough that using \cref{alg:refSeries} saves little, if any, computational effort. In this section, we consider a pair of models that differ in both the physics included and the mesh resolution, and we demonstrate computational savings using the multi-fidelity approach. In \cref{sec:setup3D_diffmesh} we describe the setup of the models and their inverse problems, and in \cref{sec:ref3D_diffmesh} we describe the results of applying \cref{alg:refSeries} to this pair of models.

@@

We now present the results of solving the inference problem using \cref{alg:refSeries}, with a relative error tolerance of $0.1\%$. At each iteration, we choose the $2\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration is usually greater than for the 2D examples. All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} \cite{libMeshPaper} (Newton's method with Brent line-search), and linear solves are performed using PETSc's \cite{petsc-user-ref} GMRES solver, preconditioned by incomplete factorization.

>>>>

\section{Numerical Experiments}\label{sec:numexp}
%
We now use \Cref{alg:refSeries} to solve goal-oriented inverse problems in a multi-model setting; the method used to localize the error estimate is described in \Cref{sec:errLocal}. We first consider two-dimensional models in order to explore the behavior of the algorithm as well as the effect of varying the placement of observations and QoI regions. In \Cref{sec:cdvcdr}, the high-fidelity model is a convection-diffusion-reaction nonlinear model, and the low-fidelity model is a linear convection-diffusion model. We apply \Cref{alg:refSeries} to this pair of models, and then examine how the localized error estimate is affected by changes in sensor placement and in the QoI region. In \Cref{sec:constvfield}, both the high- and low-fidelity models are convection-diffusion-reaction nonlinear models, but they differ in how the parameter is represented. In \Cref{sec:diffvcdr3D}, we consider a more realistic pair of three-dimensional models, again targeting a convection-diffusion-reaction problem.

@@

%------------------------------------------------------------------------------------------------------------------------%
\subsection{Variable Physics: Convection-Diffusion(-Reaction)} \label{sec:cdvcdr}
%------------------------------------------------------------------------------------------------------------------------%
In this section, we consider a pair of models which differ in the physics included. In \Cref{sec:cdvcdrSetup} we describe a baseline setup for a simple two-dimensional problem. \Cref{sec:cdvcdrBaseRef} describes the results of applying \Cref{alg:refSeries} to the baseline problem, and \Cref{sec:qoivdata} describes the results of changing the placement of the observations or the QoI region from the baseline.
%
%------------------------------------------------------------%
\subsubsection{Problem Setup} \label{sec:cdvcdrSetup}
%------------------------------------------------------------%
%
We consider a rectangular domain $\Omega(x_1,x_2)=[0,5]\times[0,1]$, where $x_1$ and $x_2$ are the spatial coordinates. The high-fidelity model is a single-species convection-diffusion-reaction equation with a nonlinear reaction term, described by,
%
\begin{subequations}
\label{eq:cdvcdrHF}
\begin{align}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2 = f(q) \quad &\text{in } \Omega, \label{eq:cdvcdrHF_int} \\
u = 0 \quad &\text{on } \partial \Omega, \label{eq:cdvcdrHF_bdry}
\end{align}
\end{subequations}
%
where the state $u$ is the species concentration and $f(q)$ is a forcing field described by the parameters. We have a divergence-free parabolic-profile velocity field $\vec{V}(x_1,x_2) = (2x_2(1-x_2),0)$; the diffusion and reaction coefficients are $k_d = 0.1$ and $k_r = -42.0$, respectively. The low-fidelity model,
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u = f(q)
\end{equation}
%
differs only in the removal of the reaction term. To form the mixed-fidelity models, we divide the domain into complementary subdomains, $\Omega_{HF}$ and $\Omega_{LF}$, where the high- and low-fidelity models are solved, respectively. The resulting mixed-fidelity models can be described by,
%
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k^{MF}_ru^2= f(q),
\end{equation}
%
where $k^{MF}_r$ is a piecewise-constant reaction coefficient,
%
\begin{equation}
k^{MF}_r=
\begin{cases}
k_r & \textrm{if }x\in\Omega_{HF} \\
0 & \textrm{if }x\in\Omega_{LF}.
\end{cases}
\end{equation}
%
Homogeneous Dirichlet boundary conditions are applied on the entire boundary of the domain. The QoI we wish to calculate is the integral of the state,
%
\begin{equation}
I(q,u)=\int_{(x_1,x_2)\in \Omega_I} u \:\textrm{d}A,
\end{equation}
%
over a region $\Omega_I=[0.625,0.875]\times[0.375,0.625]$.

The unknown parameters to be inferred correspond to the forcing field, so that in this case $f(q)=q$. The observations are sparse measurements of the state.
\Cref{fig:baseSetup} shows the locations of the observations and the region $\Omega_I$ over which the QoI is calculated. For the low-fidelity model, the inverse problem is linear (i.e., the observations depend linearly on the parameters). Since the inverse problem is ill-posed, we use Tikhonov regularization~\cite{EngHanNeu00}; the regularization term in the objective function \Cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2\:\textrm{d}A$, where $\beta=10^{-5}$ is the regularization coefficient.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/setup_3_3.pdf}
\caption{Locations of the observations and the QoI region.}
\label{fig:baseSetup}
\end{figure}
%

@@

We now present the results for solving the inference problem using \Cref{alg:refSeries}. Once the QoI error estimate is calculated using \Cref{eq:finErrExp}, the error estimate is then decomposed into local contributions. At each iteration, based on this decomposition, we choose the basis functions with the largest error contributions until an additional 5\% of the elements has been marked for refinement. This is repeated until the estimated absolute relative error in the QoI, calculated as $\epsilon_i/(\epsilon_i+I(q_{MF_i},u_{MF_i}))$, is less than $1\%$.

@@

We see that the largest local error contributions are concentrated in the QoI region and around the observation location closest to the QoI. In the first decomposition of the error (\Cref{fig:baseRef0}), the region where the elemental error is greatest is around the leftmost observation location. Since the constraining model is an elliptic PDE, with weak convection, information flow is localized, and is weakly convected from left to right. Therefore, for the calculation of the QoI, it is most important to refine the region near the leftmost observation location, and then around the QoI region. After that, the error decomposition suggests refinement in regions upstream and around the middle observation location, and then the rightmost observation location.

\Cref{fig:baseErr} shows the true and estimated absolute relative errors in the QoI for the various mixed-fidelity models generated by \Cref{alg:refSeries}; the true and estimated relative errors are calculated relative to the true and estimated high-fidelity QoI, respectively. In this case, we see that QoI error of $1\%$ is attained with a mixed-fidelity model where the high-fidelity model is used in only about $10\%$ of the domain. We note that while here the error is seen to decrease with increasing refinement, in general there is no guarantee that either the error in the QoI or the relative error in the error estimate will decrease monotonically as more of the domain is refined.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{baseSeries/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity convection-diffusion-reaction model is used.}
\label{fig:baseErr}
\end{figure}
%

@@

\Cref{fig:qoiStudy} shows the domain for three cases considered, with the same set of observations but increasingly large, nested QoI regions $\Omega_I$.
The error decompositions for each case are also shown in \Cref{fig:qoiStudy}. The bottom row gives the baseline case presented in \Cref{sec:cdvcdrBaseRef}, although here we choose the basis functions $i$ whose error $\varepsilon_i$ are among the largest $5\%$, rather than only enough basis functions to cover 5\% of the domain in their support, so the proportion of elements marked for refinement in each iteration will be slightly larger than in \Cref{sec:cdvcdrBaseRef}.
% KW: I don't understand this last sentence. What's the difference with Section 4.1.2?
Although refinement is still most important around the observation location closest to $x_1=0$, as the QoI region expands the other two observation locations become more important in that the error decomposition suggests refinement around them earlier. As the QoI region expands, it is also more clearly noticeable that refinement is not equally important in all parts of the QoI region.

\begin{figure}[htbp]
\centering
\captionsetup{justification=centering}
\subfloat[Locations of observations and QoI region $\Omega_I$][Locations of \\observations and \\QoI region $\Omega_I$]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_setup.png}
  \includegraphics[width=0.21\textwidth]{vs_qoi/vs_qoi_setup_sidetrim.png}
  \label{subfig:obsSetup}
}
\captionsetup{justification=centering}
\subfloat[MF$_0$ ($0\%$ HF)][MF$_0$ \\($0\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err0.png}
  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err0_nobar.png}
  \label{subfig:obsLF}
}
\captionsetup{justification=centering}
\subfloat[MF$_1$ ($\sim5\%$ HF)][MF$_1$ \\($\sim5\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err1.png}
  \includegraphics[width=0.16\textwidth]{vs_qoi/vs_qoi_err1_nobar.png}
}
\captionsetup{justification=centering}
\subfloat[MF$_2$ ($\sim10\%$ HF)][MF$_2$ \\($\sim10\%$ HF)]{
  %\includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2.png}
  \includegraphics[width=0.23\textwidth]{vs_qoi/vs_qoi_err2_barnorm.png}
  \label{subfig:obsMFlast}
}
  \caption{Effects of increasing the QoI region. Column \protect\subref{subfig:obsSetup}: configuration of observations (teal points) and QoI region (purple box). Columns \protect\subref{subfig:obsLF}--\protect\subref{subfig:obsMFlast}): the relative error estimate decompositions for different mixed-fidelity models, relative to the largest localized error contribution; note the locations of regions of relatively large error compared to the observation locations and QoI region.}
  \label{fig:qoiStudy}
\end{figure}

\Cref{fig:dataStudy} shows another set of cases considered, now with the same QoI region $\Omega_I$ but with increasing, nested sets of observations.
The error decomposition for the three cases is shown in \Cref{fig:dataStudy}. The bottom row is the same as that in \Cref{fig:qoiStudy}. Refinement appears to be consistently most important around the observation location closest to $x_1=0$ and the QoI region. However, as more observation locations are added, it becomes no longer necessarily true that refinement becomes less important around observation locations as their distance from the QoI region increases. In the second and third rows, one can see that after the areas around the QoI region and the two closest observation locations have been refined, the next area to be refined is not around the third closest observation location, but rather around one near the middle of the domain. This suggests that interactions between observation locations and the QoI may be non-intuitive, and in these cases a rigorous method for forming a mixed-fidelity model would be most helpful. % KW: I don't understand a lot of this discussion. You need to explain to me what you mean.

@@

We consider the same high-fidelity model as in \Cref{sec:cdvcdr}:
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in U,
\end{equation}
with the same diffusion coefficient $k_d = 0.1$  and reaction coefficient $k_r = -42$. The low-fidelity model
\begin{equation}
k_d\nabla^2 u - \vec{V}\cdot\nabla u + k_ru^2= f(q),\quad q\in\R
\end{equation}
differs from the high-fidelity model only in that the parameter $q$ is a constant instead of a field. The intermediate mixed-fidelity models thus have parameter fields that are constant over the subregions of the domain where the low-fidelity model is used. For ease of implementation, we require that the resulting parameter field remain continuous at the interface between the low-fidelity and high-fidelity subdomains, although this constraint is not necessary for the theory to hold. The domain, mesh, boundary conditions, and velocity field, as well as the observations, unknown parameters to be inferred, and QoI, remain the same as described in \Cref{sec:cdvcdr}. As the inverse problem is ill-posed, except when the low-fidelity model is used throughout the domain, regularization is used; the Tikhonov regularization term in \Cref{eq:invOpt_obj} is $R(q)=\frac{\beta}{2}\int_\Omega \|\nabla f(q)\|_2^2+f(q)^2\:\textrm{d}A$, where $\beta=10^{-3}$ is a regularization coefficient.

@@

As with the previous examples in \Cref{sec:cdvcdr}, the decomposition of the error estimate is used to select additional regions of the domain in which to use the high-fidelity model. The number of degrees of freedom in the inverse problem increases with the proportion of the domain in which the high-fidelity model is used. With each iteration, an additional $10\%$ of the elements are marked for refinement. This is repeated until the estimated absolute relative error in the QoI is less than $1\%$.

\Cref{fig:svfRef} shows the local error contributions, as well as the subdomains where the low- and high-fidelity models are used, for the first two and last mixed-fidelity model thus generated. 
%
\begin{figure}[htbp]
\centering
\subfloat[MF$_0$ ($0\%$ HF)]{
	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_LF_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_LF.png}
} \\
\subfloat[MF$_1$ ($10\%$ HF)]{
	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF01_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF01.png}
} \\
\subfloat[MF$_2$ ($20\%$ HF)]{
  \includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF02_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF02.png}
} \\
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF03_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF03.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_3$ ($30\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF04_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF04.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_4$ ($40\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
%\begin{subfigure}[b]{\textwidth}
%	\centering
%	\includegraphics[width=0.48\textwidth]{svf/cd_cdr_MF05_divvy.png}
%  \includegraphics[width=0.51\textwidth]{svf/err_breakdown_MF05.png}
%  \vspace{-0.7\baselineskip}
%  \caption{MF$_5$ ($50\%$ HF)}
%  \vspace{0.8\baselineskip}
%\end{subfigure}
\subfloat[MF$_6$ ($60\%$ HF)]{
	\includegraphics[width=0.46\textwidth]{svf/cd_cdr_MF06_divvy.png}
  \includegraphics[width=0.49\textwidth]{svf/err_breakdown_MF06.png}
}
\caption{Left: Multi-fidelity refinement over the domain (low-fidelity constant-parameter model used in red portion, high-fidelity field-parameter model used in blue portion). Right: local error contributions. The (weighted) residual, and thus the local error contribution, tends to spike sharply at the interface between the low- and high-fidelity regions; the color range is truncated to make the error distribution visible elsewhere in the domain.}
\label{fig:svfRef}
\end{figure}
%
Comparing to \Cref{fig:baseRef}, we see that in this case the local error contribution is not as greatly concentrated around the QoI region and the nearest observation location; here, all three observation locations and the QoI region have associated regions of sufficiently similar high local error that all are refined in the first iteration. This reflects the global nature of the differences between the low- and high-fidelity models.

The corresponding true and estimated absolute errors in the QoI are shown in \Cref{fig:svfErr}.
%
\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\textwidth]{svf/err_est.pdf}
\caption{True and estimated absolute relative error in QoI, plotted as a function of the percentage area of the domain in which the high-fidelity field-parameter model is used.}
\label{fig:svfErr}
\end{figure}
%
In this case, we see that we must use the high-fidelity model in most of the domain in order to get an accurate QoI. The adaptive algorithm requires us to use the field representation of the high-fidelity model in much of the left half of the domain; this reflects the topology of the inferred parameter field in the high-fidelity inverse problem, which is only relatively constant towards the right portion of the domain. We also see that in this case, in contrast to the example in \Cref{sec:cdvcdrBaseRef}, increasing the proportion of the domain in which the high-fidelity model is used does not monotonically decrease the error in the QoI.

@@

In the previous examples, although the low- and high-fidelity models are sufficiently different to illustrate the behavior of \Cref{alg:refSeries}, they are both simple enough and similar enough that using \Cref{alg:refSeries} saves little, if any, computational effort. In this section, we consider a pair of models that differ in both the physics included and the mesh resolution, and we demonstrate computational savings using the multi-fidelity approach. In \Cref{sec:setup3D_diffmesh} we describe the setup of the models and their inverse problems, and in \Cref{sec:ref3D_diffmesh} we describe the results of applying \Cref{alg:refSeries} to this pair of models.

@@

We now present the results of solving the inference problem using \Cref{alg:refSeries}, with a relative error tolerance of $0.1\%$. At each iteration, we choose the $2\%$ of the basis functions with the largest error for model refinement; since each linear Lagrange basis function has eight elements in its support, the number of additional elements marked for refinement in each iteration is usually greater than for the 2D examples. All simulations are run on a single processor; we use the default nonlinear solver in \texttt{libMesh} \cite{libMeshPaper} (Newton's method with Brent line-search), and linear solves are performed using PETSc's \cite{petsc-user-ref} GMRES solver, preconditioned by incomplete factorization.
